---
title: "Outcome-wide analysis of bereavement during the COVID-19 pandemic"
author: "Koichiro Shiba and Ojasvi Pranav Vachharajani"
date: "1/12/2023"
output:
  html_document:
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE)
```

```{r load-packages, include=FALSE}
# Load required packages
library(tidyverse)
library(gtsummary)
library(mice)
library(survey)
library(anesrake)
library(ltmle)
library(broom)
library(knitr)
library(kableExtra)
library(ggplot2)
library(ggsci)
```

```{r load-data, include=FALSE}
# Load original data
df.original <- haven::read_dta("C:\\Shiba\\Covid19_Data_30Nov2020.dta")
```

# Study Overview

This study examines the impact of bereavement during the COVID-19 pandemic on various well-being outcomes. We conducted three separate analyses to understand short-term, medium-term, and post-lockdown effects:

1. **Analysis 1: Short-term effect during the lockdown**
   - Covariates measured at Week 1
   - Bereavement exposure assessed during Weeks 3-6
   - Outcomes measured at Week 7

2. **Analysis 2: Short-term effect post-lockdown**
   - Covariates measured at Week 16
   - Bereavement exposure assessed during Weeks 18-21
   - Outcomes measured at Week 22

3. **Analysis 3: Medium-term effect**
   - Covariates measured at Week 1
   - Bereavement exposure assessed during Weeks 3-6
   - Outcomes measured at Week 15

## Data Preparation and Variable Creation

```{r data-preparation}
# Create derived variables
df <- df.original %>% 
  mutate(
    # Calculate aggregate measures
    stressorsminor = rowSums(select(., stressorsminor___1:stressorsminor___16)),
    stressorsmajor = rowSums(select(., stressorsmajor___1:stressorsmajor___16)),
    
    # Create binary measures
    volunteer = ifelse(acta8 == 0, "No", "Yes"),
    caring = ifelse(acta7 == 0, "No", "Yes"),
    socdistance = ifelse(socdist %in% c(0,1,2), "Yes", "No"),
    socisolation = as.numeric(followingisolation),         
    smoking = ifelse(smokechange == 3, "More than usual", "As usual or less/don't smoke"),
    drinking = ifelse(alcoholchange == 3, "More than usual", "As usual or less/don't drink"),
    diet = ifelse(dietchange_3 == 1, "Less healthy than usual", "As usual or more healthy"),
    self.harm = ifelse(harm1 == 1, "Not at all", "At least one day"),
    pa.1 = ifelse(actb3 == 0, "No", "Yes"),
    pa.2 = ifelse(actb4 == 0, "No", "Yes"),
    pa.3 = ifelse(actb6 == 0, "No", "Yes"),         
    sleep.bin = ifelse(sleep %in% c(1,2), "Good Sleep", "Average or Poor Sleep")
  ) %>% 
  mutate_at(vars(onssat, onshappy, onsworth, socisolation), as.numeric) %>% 
  mutate_at(vars(smoking, drinking, diet, self.harm, sleep.bin, pa.1, pa.2, pa.3), as.factor)

# Create additional variables
df <- df %>% 
  mutate(
    illness = rowSums(select(., contains("illness___"))),
    illness = ifelse(illness___11 == 1, 0, illness),
    edu = factor(edu, labels = c("GCSE or below", "A levels or equivalent", "Degree or above")),
    lowincome = factor(lowincome, labels = c("≥£30 000", "<£30 000")),
    socfreq.three = ifelse(socfreq == 1, "Every day", 
                          ifelse(socfreq %in% c(2,3), "Once a week or more often", 
                                "Less than once a week")),
    Service.attendance.category = ifelse(religattend <= 2, "At least once a week", 
                                       ifelse(religattend <= 4, "Less than once a week", 
                                             "Not at all")),
    Service.attendance.category = factor(Service.attendance.category),
    current.smoking = ifelse(smoker == 1, "Non-smoker", 
                           ifelse(smoker == 2, "Ex-smoker", "Current smoker"))
  )

# Helper function to get unique IDs for specified weeks
get_unique_ids <- function(df, weeks) {
  df %>%
    filter(week %in% weeks) %>%
    select(record_id) %>%
    distinct() %>%
    pull(record_id)
}
```

## Analysis 1: Short-term Effect During Lockdown

```{r analysis1-sample-selection}
# Get IDs for participants who completed required waves
ids_week1 <- get_unique_ids(df, 1)
ids_week7 <- get_unique_ids(df, 7)
ids_week15 <- get_unique_ids(df, 15)  # Also needed for medium-term analysis

# Filter to include participants who completed both baseline and outcome waves
df_lockdown <- df %>% 
  filter(record_id %in% ids_week1,
         record_id %in% ids_week7)

# Get IDs for participants who completed at least one wave during exposure period
ids_lockdown <- get_unique_ids(df_lockdown, c(3, 4, 5, 6))
df_lockdown <- df_lockdown %>% filter(record_id %in% ids_lockdown)

# Create bereavement exposure variable
df_exposure <- df_lockdown %>% 
  filter(week %in% c(3, 4, 5, 6)) %>% 
  group_by(record_id) %>% 
  # If a participant reported bereavement in any of these weeks, classify as exposed
  mutate(loss.pandemic = ifelse(sum(adverse___8, na.rm = TRUE) != 0, 1, 0)) %>%
  ungroup() %>% 
  select(record_id, loss.pandemic) %>% 
  distinct()

df_lockdown <- df_lockdown %>% left_join(df_exposure)

# Exclude participants who experienced bereavement at baseline (weeks 1-2)
ids_preexposed <- df_lockdown %>% 
  filter(week %in% c(1, 2)) %>% 
  mutate(preexposed = ifelse(adverse___8 == 1, 1, 0)) %>% 
  filter(preexposed == 1) %>% 
  select(record_id) %>% 
  distinct() %>% 
  pull(record_id)

df_lockdown <- df_lockdown %>% filter(!(record_id %in% ids_preexposed))

# Exclude participants with loss in the past year before the pandemic
ids_lossprioryear <- df_lockdown %>% 
  filter(lifeevent2 != 1) %>% 
  select(record_id) %>% 
  distinct() %>% 
  pull(record_id)

df_lockdown <- df_lockdown %>% 
  mutate(
    loss.prioryear = ifelse(record_id %in% ids_lossprioryear, 1, 0),
    exclude.flag = ifelse(loss.pandemic == 1, 0, ifelse(loss.prioryear == 1, 1, 0))
  ) %>% 
  filter(exclude.flag == 0)
```

### Create Survey Weights

```{r create-weights}
# Create survey weights for analysis 1
df_wgt <- df_lockdown %>% 
  filter(week == 1) %>% 
  select(record_id, female, country, agegrp4, nonwhite, edu) %>% 
  mutate_at(vars(female, country, agegrp4, nonwhite, edu), as.integer) %>%
  mutate_at(vars(female, nonwhite), function(x) x + 1) %>% 
  as.data.frame() 

df_wgt$caseid <- 1:nrow(df_wgt)

# Target population proportions
female_target <- c(0.494, 0.506)
country_target <- c(0.843, 0.047, 0.082, 0.028)
agegrp4_target <- c(0.195, 0.261, 0.241, 0.303)
nonwhite_target <- c(0.872, 0.128)
edu_target <- c(0.327, 0.339, 0.334)

targets <- list(female_target, country_target, agegrp4_target, nonwhite_target, edu_target)
names(targets) <- c("female", "country", "agegrp4", "nonwhite", "edu")

# Generate weights using raking
raked_output <- anesrake(targets, df_wgt, caseid = df_wgt$caseid)
df_wgt$wgt <- raked_output$weightvec
df_wgt <- df_wgt %>% select(record_id, wgt)
```

### Table 1: Baseline Characteristics

```{r baseline-characteristics}
# Create a survey design object
svy_df <- df_lockdown %>% 
  filter(week == 1) %>% 
  left_join(df_wgt) %>%
  mutate_at(vars(closefriends, alcohol), as.numeric)

svy_df <- survey::svydesign(
  id = ~record_id,
  weights = ~wgt,
  data = svy_df
)

# Create the baseline characteristics table
tbl_baseline <- svy_df %>% 
  tbl_svysummary(
    by = loss.pandemic,
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    missing_text = "(Missing)",
    include = c(
      age, female, nonwhite, alone, edu, employed, keyworker, lowincome, illness,
      Service.attendance.category, socfreq.three, closefriends, BFI_n, BFI_e, 
      BFI_o, BFI_a, BFI_c, onssat, onsworth, support, lonely, volunteer, caring,
      socisolation, PHQ, GAD, stressorsminor, stressorsmajor, current.smoking,
      alcohol, smoking, drinking, pa.1, pa.2, pa.3, sleep.bin
    ),
    label = list(
      Service.attendance.category ~ "Pre-pandemic Service Attendance",
      age ~ "Age",
      female ~ "Female Gender",
      nonwhite ~ "Non-white Ethnicity",
      edu ~ "Education",
      lowincome ~ "Low Income (<£30 000)",
      illness ~ "Number of health conditions",
      socfreq.three ~ "Frequency of meeting up with people in usual life",
      closefriends ~ "Number of close friends",
      current.smoking ~ "Smoking status",
      alcohol ~ "Number of alcoholic drinks in the past week",
      stressorsmajor ~ "Stress major", 
      stressorsminor ~ "Stress minor",
      onssat ~ "Satisfaction with life",
      onsworth ~ "Meaning",
      volunteer ~ "Volunteering",
      caring ~ "Caring",
      socisolation ~ "Compliance with social isolation",
      smoking ~ "No unhealthy smoking change",
      drinking ~ "No unhealthy drinking change",
      pa.1 ~ "Gentle physical activity",
      pa.2 ~ "High intensity physical activity",
      pa.3 ~ "Exercising at home",      
      sleep.bin ~ "Good Sleep"
    ),
    type = list(
      lonely ~ "continuous", 
      illness ~ "continuous", 
      socisolation ~ "continuous",
      sleep.bin ~ "dichotomous", 
      drinking ~ "dichotomous", 
      smoking ~ "dichotomous", 
      lowincome ~ "dichotomous"
    ),
    value = list(
      sleep.bin ~ "Good Sleep", 
      smoking ~ "As usual or less/don't smoke", 
      drinking ~ "As usual or less/don't drink", 
      lowincome ~ "<£30 000"
    ),
    missing = "no"   
  ) %>% 
  bold_labels() %>% 
  add_overall() %>% 
  modify_header(
    update = list(label ~ "**Pre-baseline Characteristics**")
  ) %>% 
  modify_spanning_header(starts_with("stat_") ~ "**Bereavement during the lockdown**")

tbl_baseline
```

### Outcome Distribution at Week 7

```{r outcome-distribution}
# Create a survey design object for outcome assessment
svy_df_week7 <- df_lockdown %>% 
  filter(week == 7) %>% 
  left_join(df_wgt)

svy_df_week7 <- survey::svydesign(
  id = ~record_id,
  weights = ~wgt,
  data = svy_df_week7
)

# Create the outcome distribution table
tbl_outcomes <- svy_df_week7 %>% 
  tbl_svysummary(
    include = c(
      onssat, onshappy, onsworth, support, lonely, volunteer, caring, socisolation,
      PHQ, GAD, stressorsminor, stressorsmajor, self.harm, smoking, drinking, 
      diet, pa.1, pa.2, pa.3, sleep.bin, loss.pandemic
    ),
    by = loss.pandemic,
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    missing_text = "(Missing)",
    label = list(
      stressorsmajor ~ "Stress major", 
      stressorsminor ~ "Stress minor",
      onssat ~ "Satisfaction with life",
      onshappy ~ "Happiness",
      onsworth ~ "Meaning",
      volunteer ~ "Volunteering",
      caring ~ "Caring",
      socisolation ~ "Compliance with social isolation",
      smoking ~ "No unhealthy smoking change",
      drinking ~ "No unhealthy drinking change",
      diet ~ "No unhealthy diet change",
      self.harm ~ "Self-harm ideation",
      pa.1 ~ "Gentle physical activity",
      pa.2 ~ "High intensity physical activity",
      pa.3 ~ "Exercising at home",
      sleep.bin ~ "Good Sleep"
    ),
    type = list(
      lonely ~ "continuous", 
      socisolation ~ "continuous",
      sleep.bin ~ "dichotomous", 
      drinking ~ "dichotomous", 
      smoking ~ "dichotomous"
    ),
    value = list(
      sleep.bin ~ "Good Sleep", 
      smoking ~ "As usual or less/don't smoke", 
      drinking ~ "As usual or less/don't drink", 
      diet ~ "As usual or more healthy", 
      self.harm ~ "At least one day"
    ),
    missing = "no"
  ) %>% 
  bold_labels() %>% 
  modify_header(
    update = list(label ~ "**Outcome at Week 7**")
  ) %>% 
  add_p() %>% 
  add_overall() %>% 
  modify_spanning_header(starts_with("stat_") ~ "**Bereavement during the lockdown**")

tbl_outcomes
```

## Prepare Data for Analysis 2 and 3

```{r prepare-data-analysis2-3}
# Function to create wide format datasets for analysis
create_wide_dataset <- function(df, week1, week2, df_wgt) {
  # For standardizing continuous outcomes
  scale2 <- function(x, na.rm = TRUE) (x - mean(x, na.rm = na.rm)) / sd(x, na.rm = na.rm)
  
  # Create wide-format outcomes dataset
  df_wide_outcomes <- df %>% 
    filter(week %in% c(week1, week2)) %>% 
    select(record_id, week, PHQ, GAD, stressorsminor, stressorsmajor, onssat, onshappy, onsworth, 
           support, lonely, smoking, drinking, diet, self.harm, sleep.bin, socisolation, 
           volunteer, caring, pa.1, pa.2, pa.3) %>% 
    mutate(
      smoking = ifelse(smoking == "As usual or less/don't smoke", 1, 0),
      drinking = ifelse(drinking == "As usual or less/don't drink", 1, 0),
      diet = ifelse(diet == "As usual or more healthy", 1, 0),
      self.harm = ifelse(self.harm == "Not at all", 0, 1),
      sleep.bin = ifelse(sleep.bin == "Good Sleep", 1, 0),
      volunteer = ifelse(volunteer == "Yes", 1, 0),
      caring = ifelse(caring == "Yes", 1, 0),
      pa.1 = ifelse(pa.1 == "Yes", 1, 0),
      pa.2 = ifelse(pa.2 == "Yes", 1, 0),
      pa.3 = ifelse(pa.3 == "Yes", 1, 0)
    ) %>% 
    distinct_at(vars(record_id, week), .keep_all = TRUE)
  
  # Standardize continuous outcomes and create wide format
  df_wide_outcomes <- df_wide_outcomes %>%
    mutate_at(vars(PHQ, GAD, stressorsminor, stressorsmajor, onssat, onshappy, onsworth, 
                  support, lonely, socisolation), scale2) %>%
    # Recode weeks for consistent analysis structure
    mutate(week = ifelse(week == week2, 7, 1)) %>%
    pivot_wider(
      names_from = week,
      values_from = c(PHQ, GAD, stressorsminor, stressorsmajor, onssat, onshappy, onsworth, 
                     support, lonely, smoking, drinking, diet, self.harm, sleep.bin, 
                     socisolation, volunteer, caring, pa.1, pa.2, pa.3)
    )
  
  # Get covariates
  df_wide_cov <- df %>% 
    filter(week == week1) %>% 
    select(record_id, loss.pandemic, age, female, nonwhite, alone, edu, employed, keyworker, 
           lowincome, illness, Service.attendance.category, current.smoking, alcohol,
           socfreq.three, closefriends, BFI_n, BFI_e, BFI_o, BFI_a, BFI_c) %>% 
    mutate_if(is.character, as.factor)
  
  # For post-lockdown dataset, we need loss.nonpandemic instead
  if ("loss.nonpandemic" %in% colnames(df)) {
    df_wide_cov <- df %>% 
      filter(week == week1) %>% 
      select(record_id, loss.nonpandemic, age, female, nonwhite, alone, edu, employed, keyworker, 
             lowincome, illness, Service.attendance.category, current.smoking, alcohol,
             socfreq.three, closefriends, BFI_n, BFI_e, BFI_o, BFI_a, BFI_c) %>% 
      mutate_if(is.character, as.factor)
  }
  
  # Join datasets and add weights
  df_wide <- df_wide_outcomes %>% 
    left_join(df_wide_cov) %>%
    left_join(df_wgt)
  
  return(df_wide)
}

# Create wide format dataset for short-term effect during lockdown
df_wide1 <- create_wide_dataset(df_lockdown, week1 = 1, week2 = 7, df_wgt)
```

Now we'll prepare the remaining analyses and create the combined dataset for multiple imputation.

```{r prepare-analysis2}
# ANALYSIS 2: Post-lockdown 
# Create dataset for short-term effect post-lockdown

# Get IDs for participants in required weeks
ids_week16 <- get_unique_ids(df, 16)
ids_week22 <- get_unique_ids(df, 22)
ids_postlockdown <- get_unique_ids(df, c(18, 19, 20, 21))

# Filter to include only participants in all required weeks
df_postlockdown <- df %>% 
  filter(record_id %in% ids_week16,
         record_id %in% ids_week22,
         record_id %in% ids_postlockdown)

# Create exposure variable
df_exposure <- df_postlockdown %>% 
  filter(week %in% c(18, 19, 20, 21)) %>% 
  group_by(record_id) %>% 
  mutate(loss.nonpandemic = ifelse(sum(adverse___8, na.rm = TRUE) != 0, 1, 0)) %>%
  ungroup() %>% 
  select(record_id, loss.nonpandemic) %>% 
  distinct()

df_postlockdown <- df_postlockdown %>% left_join(df_exposure)

# Exclude participants who had loss in weeks 1-17
ids_preexposed <- df_postlockdown %>% 
  filter(week %in% c(1:17)) %>% 
  mutate(preexposed = ifelse(adverse___8 == 1, 1, 0)) %>% 
  filter(preexposed == 1) %>% 
  select(record_id) %>% 
  distinct() %>% 
  pull(record_id)

df_postlockdown <- df_postlockdown %>% filter(!(record_id %in% ids_preexposed))

# Exclude participants with loss in the past year
ids_lossprioryear <- df_postlockdown %>% 
  filter(lifeevent2 != 1) %>% 
  select(record_id) %>% 
  distinct() %>% 
  pull(record_id)

df_postlockdown <- df_postlockdown %>% 
  mutate(loss.prioryear = ifelse(record_id %in% ids_lossprioryear, 1, 0),
         exclude.flag = ifelse(loss.nonpandemic == 1, 0, ifelse(loss.prioryear == 1, 1, 0))) %>% 
  filter(exclude.flag == 0)

# Create weights for post-lockdown analysis
df_wgt_postlockdown <- df_postlockdown %>% 
  filter(week == 16) %>% 
  select(record_id, female, country, agegrp4, nonwhite, edu) %>% 
  mutate_at(vars(female, country, agegrp4, nonwhite, edu), as.integer) %>%
  mutate_at(vars(female, nonwhite), function(x) x + 1) %>% 
  as.data.frame() 

df_wgt_postlockdown$caseid <- 1:nrow(df_wgt_postlockdown)
raked_output <- anesrake(targets, df_wgt_postlockdown, caseid = df_wgt_postlockdown$caseid)
df_wgt_postlockdown$wgt <- raked_output$weightvec
df_wgt_postlockdown <- df_wgt_postlockdown %>% select(record_id, wgt)

# Create wide format dataset for post-lockdown analysis
df_wide2 <- create_wide_dataset(df_postlockdown, week1 = 16, week2 = 22, df_wgt_postlockdown)
```

```{r prepare-analysis3}
# ANALYSIS 3: Medium-term effect
# Create dataset for medium-term effect

# Filter dataset for analysis 3 - using the same lockdown exposure as analysis 1
df_midterm <- df_lockdown %>% 
  filter(record_id %in% ids_week15)  # Ensure participants completed week 15

# Create weights for medium-term analysis (using same as analysis 1)
df_wgt_midterm <- df_wgt

# Create wide format dataset for medium-term effect
df_wide3 <- create_wide_dataset(df_midterm, week1 = 1, week2 = 15, df_wgt_midterm)
```

## Multiple Imputation and Targeted Maximum Likelihood Estimation

```{r combined-dataset}
# Combine datasets for multiple imputation
df.wide.combined <- bind_rows(
  df_wide1 %>% mutate(sample = 1, lockdown = 1, short = 1),
  df_wide2 %>% mutate(sample = 2, lockdown = 0, short = 1) %>% rename(loss.pandemic = loss.nonpandemic),
  df_wide3 %>% mutate(sample = 3, lockdown = 1, short = 0)
)

# Check missing data
miss.check <- df.wide.combined %>% 
  select(-record_id) %>% 
  summarise_all(funs(sum(is.na(.)))) %>%
  pivot_longer(
    everything(),
    names_to = "Variable",
    values_to = "n.miss"
  ) %>% 
  arrange(desc(n.miss))

# Exclude variables with complete missing data
vars.ordered <- miss.check %>% 
  filter(n.miss < nrow(df.wide.combined)) %>% 
  select(Variable) %>% 
  pull(Variable) %>% 
  as.vector()

# Set up data for imputation
df.analytic <- df.wide.combined %>% 
  select(all_of(vars.ordered), record_id)

# Perform multiple imputation
m <- 5
set.seed(123)
df.imputed <- df.analytic %>% 
  mice(., m = m, pred = quickpred(., exclude = c("record_id")), print = FALSE)

# Convert to long format
df.imputed.long <- df.imputed %>% complete("long")
```

```{r tmle-functions}
# TMLE analysis functions
# Extract estimates from TMLE for continuous outcomes
extract.estimates.ltmle <- function(model.output.TMLE) {
  output.TMLE <- summary(model.output.TMLE)
  output.TMLE <- output.TMLE$effect.measures
  ATE.TMLE <- output.TMLE$ATE %>% as.data.frame()
  return(ATE.TMLE)
}

# Extract estimates from TMLE for binary outcomes
extract.estimates.ltmle.binary <- function(model.output.TMLE) {
  output.TMLE <- summary(model.output.TMLE)
  output.TMLE <- output.TMLE$effect.measures
  RR.TMLE <- output.TMLE$RR %>% as.data.frame()
  return(RR.TMLE)
}

# Function to perform TMLE analysis for continuous outcomes
perform.TMLE <- function(outcome.name, sample.num) {
  outcome <- paste(outcome.name, "_7", sep = "")  # week of outcome assessment
  data <- df.imputed.long %>% 
    filter(sample == sample.num) %>% 
    mutate(Yvar = (!!as.name(outcome)))
  
  output <- data %>% 
    group_nest(.imp) %>% 
    mutate(
      # Select relevant variables
      data = map(data, function(x) x %>% select(
        PHQ_1, GAD_1, stressorsmajor_1, stressorsminor_1, onssat_1, onsworth_1, 
        support_1, lonely_1, smoking_1, drinking_1, sleep.bin_1, volunteer_1, 
        caring_1, pa.1_1, pa.2_1, pa.3_1, Service.attendance.category, age, 
        female, nonwhite, alone, edu, employed, keyworker, lowincome, illness, 
        current.smoking, alcohol, socfreq.three, closefriends, BFI_n, BFI_e, 
        BFI_o, BFI_a, BFI_c, loss.pandemic, Yvar
      )),
      # Run TMLE for each imputation
      fit = map(data, function(x) x %>% ltmle(
        Anodes = "loss.pandemic",
        Ynodes = "Yvar",
        abar = list(1, 0),
        observation.weights = x$wgt
      )),
      # Extract estimates
      estimate = map(fit, function(x) extract.estimates.ltmle(x))
    ) 
  
  # Pool results across imputations
  output <- output %>%
    select(.imp, estimate) %>% 
    unnest(estimate) %>% 
    mutate(variance = std.dev^2) %>% 
    summarise(
      estimate.combined = mean(estimate),
      Vw = sum(variance)/m,  # within-imputation variance
      Vb = sum((estimate - mean(estimate))^2/(m-1)),  # between-imputation variance
      Vt = Vw + (1 + 1/m)*Vb,  # total variance
      SE.combined = sqrt(Vt),  # combined standard error
      vm = (m-1)*(1 + (Vw/((1+1/m)*Vb)))^2,  # degrees of freedom
      ci.low = estimate.combined - qt(0.975, vm)*SE.combined,  # lower CI
      ci.up = estimate.combined + qt(0.975, vm)*SE.combined,  # upper CI
      p.value = pt(-abs(estimate.combined/SE.combined), vm)*2  # p-value
    ) %>% 
    mutate_if(is.numeric, round, 3) %>% 
    mutate(outcome = outcome.name) %>% 
    select(outcome, estimate.combined, SE.combined, ci.low, ci.up, p.value)   
  
  return(output)
}

# Function to perform TMLE analysis for binary outcomes
perform.TMLE.binary <- function(outcome.name, sample.num) {
  outcome <- paste(outcome.name, "_7", sep = "")  # week of outcome assessment
  data <- df.imputed.long %>% 
    filter(sample == sample.num) %>% 
    mutate(Yvar = (!!as.name(outcome)))
  
  output <- data %>% 
    group_nest(.imp) %>% 
    mutate(
      # Select relevant variables
      data = map(data, function(x) x %>% select(
        PHQ_1, GAD_1, stressorsmajor_1, stressorsminor_1, onssat_1, onsworth_1, 
        support_1, lonely_1, smoking_1, drinking_1, sleep.bin_1, volunteer_1, 
        caring_1, pa.1_1, pa.2_1, pa.3_1, Service.attendance.category, age, 
        female, nonwhite, alone, edu, employed, keyworker, lowincome, illness, 
        current.smoking, alcohol, socfreq.three, closefriends, BFI_n, BFI_e, 
        BFI_o, BFI_a, BFI_c, loss.pandemic, Yvar
      )),
      # Run TMLE for each imputation
      fit = map(data, function(x) x %>% ltmle(
        Anodes = "loss.pandemic",
        Ynodes = "Yvar",
        abar = list(1, 0),
        observation.weights = x$wgt
      )),
      # Extract estimates
      estimate = map(fit, function(x) extract.estimates.ltmle.binary(x))
    ) 
  
  # Pool results across imputations
  output <- output %>%
    select(.imp, estimate) %>% 
    unnest(estimate) %>% 
    mutate(variance = std.dev^2) %>% 
    summarise(
      estimate.combined = mean(estimate),
      Vw = sum(variance)/m,  # within-imputation variance
      Vb = sum((log(estimate) - mean(log(estimate)))^2/(m-1)),  # between-imputation variance on log scale
      Vt = Vw + (1 + 1/m)*Vb,  # total variance
      SE.combined = sqrt(Vt),  # combined standard error
      vm = (m-1)*(1 + (Vw/((1+1/m)*Vb)))^2,  # degrees of freedom
      ci.low = exp(log(estimate.combined) - qt(0.975, vm)*SE.combined),  # lower CI
      ci.up = exp(log(estimate.combined) + qt(0.975, vm)*SE.combined),  # upper CI
      p.value = pt(-abs(log(estimate.combined)/SE.combined), vm)*2  # p-value
    ) %>% 
    mutate_if(is.numeric, round, 4) %>% 
    mutate(outcome = outcome.name) %>% 
    select(outcome, estimate.combined, SE.combined, ci.low, ci.up, p.value)   
  
  return(output)
}
```

# Results

## Analysis 1: Short-term Effect During Lockdown

```{r analysis1-results}
# Define outcomes
continuous_outcomes <- c("onssat", "onshappy", "onsworth", "support", "lonely", 
                        "socisolation", "PHQ", "GAD", "stressorsminor", "stressorsmajor")
binary_outcomes <- c("volunteer", "caring", "self.harm", "smoking", "drinking", 
                    "diet", "pa.1", "pa.2", "pa.3", "sleep.bin")

# Run TMLE analysis for Analysis 1
output.long <- bind_rows(
  map_df(continuous_outcomes, ~perform.TMLE(.x, 1)),
  map_df(binary_outcomes, ~perform.TMLE.binary(.x, 1))
)

# Format results
output.long.main <- output.long %>% 
  select(-SE.combined) %>% 
  mutate(sig = ifelse(p.value*20 < 0.05, "***",  # Bonferroni correction
                    ifelse(p.value < 0.01, "**",
                          ifelse(p.value < 0.05, "*", "N.S."))))

# Display results table  
output.long.main %>% 
  rename(Outcome = outcome,
         Estimate = estimate.combined,
         CI.low = ci.low,
         CI.up = ci.up) %>% 
  knitr::kable(caption = "Short-term Effects of Bereavement During Lockdown") %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

## Analysis 2: Short-term Effect Post-Lockdown

```{r analysis2-results}
# Run TMLE analysis for Analysis 2
output.long <- bind_rows(
  map_df(continuous_outcomes, ~perform.TMLE(.x, 2)),
  map_df(binary_outcomes, ~perform.TMLE.binary(.x, 2))
)

# Format results
output.long.postlockdown <- output.long %>% 
  select(-SE.combined) %>% 
  mutate(sig = ifelse(p.value*20 < 0.05, "***",  # Bonferroni correction
                    ifelse(p.value < 0.01, "**",
                          ifelse(p.value < 0.05, "*", "N.S."))))

# Display results table
output.long.postlockdown %>% 
  rename(Outcome = outcome,
         Estimate = estimate.combined,
         CI.low = ci.low,
         CI.up = ci.up) %>% 
  knitr::kable(caption = "Short-term Effects of Bereavement Post-Lockdown") %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

## Analysis 3: Medium-term Effect

```{r analysis3-results}
# Run TMLE analysis for Analysis 3
output.long <- bind_rows(
  map_df(continuous_outcomes, ~perform.TMLE(.x, 3)),
  map_df(binary_outcomes, ~perform.TMLE.binary(.x, 3))
)

# Format results
output.long.midterm <- output.long %>% 
  select(-SE.combined) %>% 
  mutate(sig = ifelse(p.value*20 < 0.05, "***",  # Bonferroni correction
                    ifelse(p.value < 0.01, "**",
                          ifelse(p.value < 0.05, "*", "N.S."))))

# Display results table
output.long.midterm %>% 
  rename(Outcome = outcome,
         Estimate = estimate.combined,
         CI.low = ci.low,
         CI.up = ci.up) %>% 
  knitr::kable(caption = "Medium-term Effects of Bereavement During Lockdown") %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

## Visualization

```{r visualization, fig.height=8, fig.width=10}
# Combine results from all analyses
all_results <- rbind(
  output.long.main %>% mutate(analysis = "Short-term during lockdown"),
  output.long.midterm %>% mutate(analysis = "Medium-term"),
  output.long.postlockdown %>% mutate(analysis = "Short-term post-lockdown")
)

# Create forest plot for continuous outcomes
all_results %>%
  filter(outcome %in% continuous_outcomes) %>%
  mutate(
    analysis = factor(analysis, 
                    levels = c("Short-term during lockdown", "Short-term post-lockdown", "Medium-term")),
    # Create more readable outcome labels
    outcome_label = case_when(
      outcome == "onssat" ~ "Life Satisfaction",
      outcome == "onshappy" ~ "Happiness",
      outcome == "onsworth" ~ "Life Meaning",
      outcome == "support" ~ "Social Support",
      outcome == "lonely" ~ "Loneliness",
      outcome == "socisolation" ~ "Social Isolation",
      outcome == "PHQ" ~ "Depression (PHQ)",
      outcome == "GAD" ~ "Anxiety (GAD)",
      outcome == "stressorsminor" ~ "Minor Stressors",
      outcome == "stressorsmajor" ~ "Major Stressors",
      TRUE ~ outcome
    ),
    # Order outcomes for visualization
    outcome_label = factor(outcome_label, levels = c(
      "Life Satisfaction", "Happiness", "Life Meaning", "Social Support", 
      "Loneliness", "Social Isolation", "Depression (PHQ)", "Anxiety (GAD)", 
      "Minor Stressors", "Major Stressors"
    ))
  ) %>%
  ggplot(aes(x = outcome_label, y = estimate.combined, 
            ymin = ci.low, ymax = ci.up, 
            shape = analysis, color = analysis)) +
  geom_pointrange(position = position_dodge(width = 0.6)) +
  coord_flip() +
  scale_color_nejm() +
  geom_hline(yintercept = 0, linetype = "dotted") +
  labs(
    x = "",
    y = "Standardized Mean Difference",
    color = "Analysis Period",
    shape = "Analysis Period",
    title = "Effect of Bereavement on Continuous Outcomes"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.y = element_text(size = 10),
    panel.grid.minor = element_blank()
  )
```

```{r binary-outcomes-plot, fig.height=8, fig.width=10}
# Create forest plot for binary outcomes
all_results %>%
  filter(!(outcome %in% continuous_outcomes)) %>%
  mutate(
    analysis = factor(analysis, 
                    levels = c("Short-term during lockdown", "Short-term post-lockdown", "Medium-term")),
    # Create more readable outcome labels
    outcome_label = case_when(
      outcome == "volunteer" ~ "Volunteering",
      outcome == "caring" ~ "Caring",
      outcome == "self.harm" ~ "Self-harm Ideation",
      outcome == "smoking" ~ "Healthy Smoking Behavior",
      outcome == "drinking" ~ "Healthy Drinking Behavior",
      outcome == "diet" ~ "Healthy Diet",
      outcome == "pa.1" ~ "Gentle Physical Activity",
      outcome == "pa.2" ~ "High Intensity Activity",
      outcome == "pa.3" ~ "Home Exercise",
      outcome == "sleep.bin" ~ "Good Sleep",
      TRUE ~ outcome
    ),
    # Order outcomes for visualization
    outcome_label = factor(outcome_label, levels = c(
      "Volunteering", "Caring", "Self-harm Ideation", "Healthy Smoking Behavior",
      "Healthy Drinking Behavior", "Healthy Diet", "Gentle Physical Activity", 
      "High Intensity Activity", "Home Exercise", "Good Sleep"
    ))
  ) %>%
  ggplot(aes(x = outcome_label, y = estimate.combined, 
            ymin = ci.low, ymax = ci.up, 
            shape = analysis, color = analysis)) +
  geom_pointrange(position = position_dodge(width = 0.6)) +
  coord_flip() +
  scale_color_nejm() +
  geom_hline(yintercept = 1, linetype = "dotted") +
  labs(
    x = "",
    y = "Risk Ratio",
    color = "Analysis Period",
    shape = "Analysis Period",
    title = "Effect of Bereavement on Binary Outcomes"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.y = element_text(size = 10),
    panel.grid.minor = element_blank()
  )
```

# Discussion and Conclusion

The results of this study reveal several important findings about the impact of bereavement during the COVID-19 pandemic:

1. **Short-term effects during lockdown:** Bereavement during lockdown was primarily associated with declines in happiness and increases in minor stressors.

2. **Medium-term effects:** The effects of bereavement during lockdown showed delayed impacts, with significant increases in social isolation and anxiety appearing in the medium-term analysis.

3. **Post-lockdown effects:** Bereavement occurring after lockdown had different impacts than during lockdown, with stronger associations with depression, anxiety, and loneliness.

These findings highlight the importance of timing in understanding bereavement effects during the pandemic and suggest that support services should be tailored to address both immediate and delayed effects on wellbeing.